### 2021-06-09 paper/report.tex
Remove decomposition plots in the beginning.
Fixed some typos and added a comment.

\begin{figure}
\centering
        \includegraphics[width=\textwidth]{../figures/results/figures/full_decomposition_rapid_tests_area}
        \caption{Decomposition of Rapid Tests}
\end{figure}
\begin{figure}
\centering
        \includegraphics[width=\textwidth]{../figures/results/figures/full_decomposition_rapid_tests_bar}
        \caption{Decomposition of Rapid Tests}
\end{figure}

@@

The model includes several other features, which are crucial to describe the evolution
of the pandemic in 2020-2021. New virus strains with different profiles regarding
infectiousness can be introduced. Agents may receive a vaccination. With a probability
of 75\% \citep{Hunter2021}, vaccinated agents become immune and they do not transmit the
virus \citep{Petter2021, LevineTiefenbrun2021, Pritchard2021}.\footnote{75\% is lower
than what is usually reported for after the second dose of the Biontech/Pfizer vaccine,
which is most commonly used in Germany. We choose it because our model neither includes
booster shots, nor does it allow vaccinated individuals who became immune to transmit
the disease\citep{Petter2021, LevineTiefenbrun2021, Pritchard2021}.} During the vaccine
roll-out, priority may depend on age and occupation.

We include two types of tests. Polymerase chain reaction (PCR) tests directly reveal
whether an individual is infected or not. PCR tests require some days to be processed
and there are always aggregate capacity constraints. In contrast, rapid antigen tests
yield immediate results. Specificity and sensitivity of these tests is set according to
data analysed in \cite{Bruemmer2021, Smith2021}; sensitivity depends on the timing of
the test relative to the start of infectiousness. Figure~\ref{fig:antigen_tests} shows
our model for rapid test demand. Schools may require students to be tested regularly.
Rapid tests may be offered by employers for on-site workers. Individuals may demand
tests for private reasons, which include having plans to meet other people\footnote{A
positive test will make them reduce their contacts; this is why tests impact the actual
contacts in Figure~\ref{fig:model-description}.}, showing symptoms of CoViD-19, and
because a household member tested positively for the virus. We endow each agent with an
individual compliance parameter. This parameter determines whether she takes up rapid
tests offered by employers or follows up on private reasons. The thresholds are lower
for tests in a private setting than for tests at the workplace.\comment[id=HM]{True?
@Janos}

@@

We apply this model to Germany. In March and April 2020, the country broke the first
wave of the pandemic fairly quickly. Between May and mid-September, daily new infections
were below 20 per Million and day \citep{owidcoronavirus}. We model the period
mid-September 2020 to the end of May 2021. We pick the starting date for two reasons.
First, we do not include the first wave because the environment was very different
(e.g., aggregate PCR test capacity was much lower and we would require a very different
model for calculating the share of known cases) Second, a large fraction cases during
summer of 2020 were traced to international travel \citep{KochInstitut2021,Hodcroft2021}
but the precise number is difficult to model.

>>>>

@@

The model includes several other features, which are crucial to describe the evolution
of the pandemic in 2020-2021. New virus strains with different profiles regarding
infectiousness can be introduced. Agents may receive a vaccination. With a probability
of 75\% \citep{Hunter2021}, vaccinated agents become immune and they do not transmit the
virus \citep{Petter2021, LevineTiefenbrun2021, Pritchard2021}.\comment[id=T]{Maybe add
that 35\% reach immunity after two weeks and 40\% after three weeks.}\footnote{75\% is
lower than what is usually reported for after the second dose of the Biontech/Pfizer
vaccine, which is most commonly used in Germany. We choose it because our model neither
includes booster shots, nor does it allow vaccinated individuals who became immune to
transmit the disease \citep{Petter2021, LevineTiefenbrun2021, Pritchard2021}.} During
the vaccine roll-out, priority may depend on age and occupation.

We include two types of tests. Polymerase chain reaction (PCR) tests directly reveal
whether an individual is infected or not. PCR tests require some days to be processed
and there are always aggregate capacity constraints. In contrast, rapid antigen tests
yield immediate results. Specificity and sensitivity of these tests is set according to
data analyzed in \cite{Bruemmer2021, Smith2021}; sensitivity depends on the timing of
the test relative to the start of infectiousness. Figure~\ref{fig:antigen_tests} shows
our model for rapid test demand. Schools may require students to be tested regularly.
Rapid tests may be offered by employers for on-site workers. Individuals may demand
tests for private reasons, which include having plans to meet other people\footnote{A
positive test will make them reduce their contacts; this is why tests impact the actual
contacts in Figure~\ref{fig:model-description}.}, showing symptoms of CoViD-19, and
because a household member tested positively for the virus. We endow each agent with an
individual compliance parameter. This parameter determines whether she takes up rapid
tests offered by employers or follows up on private reasons. The thresholds are lower
for tests in a private setting than for tests at the workplace.\comment[id=HM]{True?
@Janos}

@@

We apply this model to Germany. In March and April 2020, the country broke the first
wave of the pandemic fairly quickly. Between May and mid-September, daily new infections
were below 20 per Million and day \citep{owidcoronavirus}. We model the period
mid-September 2020 to the end of May 2021. We pick the starting date for two reasons.
First, we do not include the first wave because the environment was very different
(e.g., aggregate PCR test capacity was much lower and we would require a very different
model for calculating the share of known cases). Second, a large fraction of cases
during summer of 2020 were traced to international travel
\citep{KochInstitut2021,Hodcroft2021} but the precise number is difficult to model.
